Hyper-linked Communications: WebRTC enabled asynchronous collaboration

### 2016-05-22 tese2/15_implementation_recording.tex
[FIX] front cover typo

	With server side recording, the user would maintain always the same stream \ac{URL} even if it is playing real-time video or reproducing recorded video. It is \ac{KMS} that sends different content through that stream. When a user desires to play recorded video, a \emph{webSocket} message is sent specifying the time and the intended user id. The group identification is not sent because it is already associated to the \emph{webSocket}. The server performs the same calculations in order to find a block that intersects the requested time, plays it and when finished, the next part is automatically played without the user intervention.

@@

	If we choose the closest chunk to play this lead to a playing time error that can be at most half the duration of a block, as it can be seen on figure \ref{fig:nearchunkerror} where the black dot represents the requested time to play. In this case, which is the worst, either $ block_{n}$ or $ block_{n+1}$ (with duration $d$) can be played from their beginning with a maximum error ($e$) correspondent to half their duration ($\frac{d}{2}$) .

	In practice, the maximum playing time error coincides with the block duration because we must show always what the user requests, as it can be seen on figure \ref{fig:interchunkerror}. In this case, if a user wishes to play a time that is close to the end of $block_n$ the maximum playing error ($e$) is at most the chunk's duration ($d$) because we have to play $block_n$ from its beginning.
        %RP já tinhamos falado sobre isto. O erro é no máximo o tamanho do bloco pois queres garantir que a pessoa ve sempre o que solicita. Assim começas sempre no bloco que fica antes e nunca no que fica depois.

>>>>

	With server side recording, the user would maintain always the same stream \ac{URL} even if it is playing real time video or reproducing recorded video. It is \ac{KMS} that sends different content through that stream. When a user desires to play recorded video, a \emph{webSocket} message is sent specifying the time and the intended user id. The group identification is not sent because it is already associated to the \emph{webSocket}. The server performs the same calculations in order to find a block that intersects the requested time, plays it and when finished, the next part is automatically played without the user intervention.

@@

	If we choose the closest chunk to play this lead to a playing time error that can be at most half the duration of a block, as it can be seen on Figure \ref{fig:nearchunkerror} where the black dot represents the requested time to play. In this case, which is the worst, either $ block_{n}$ or $ block_{n+1}$ (with duration $d$) can be played from their beginning with a maximum error ($e$) correspondent to half their duration ($\frac{d}{2}$) .

	In practice, the maximum playing time error coincides with the block duration because we must show always what the user requests, as it can be seen on Figure \ref{fig:interchunkerror}. In this case, if a user wishes to play a time that is close to the end of $block_n$ the maximum playing error ($e$) is at most the chunk's duration ($d$) because we have to play $block_n$ from its beginning.
        %RP já tinhamos falado sobre isto. O erro é no máximo o tamanho do bloco pois queres garantir que a pessoa ve sempre o que solicita. Assim começas sempre no bloco que fica antes e nunca no que fica depois.

### 2016-05-22 tese2/16_implementation_content.tex
caneco
[FIX] front cover typo

	In order to create content, the user has the option to write simple movie captions without writing any code, otherwise, as mentioned before, it can write \ac{HTML}, \ac{CSS} and \emph{JavaScript}. The definition of the content's starting and ending time by the user it's not an easy task. 
	Figure \ref{fig:creation} shows the user interface for creating interactive hyper content manually.

@@

	Defining the content's time to appear in real-time would require a previous user plan. Otherwise the user could make a speech and insert the content later.

	As manually content insertion is a laborious task that can be realized after the video is recorder, we provide an alternative mechanism for real time introduction of superimposed content.	In order to help the content creator to introduce and synchronize its content in real-time, we allow the user to encode its content into \ac{QR} codes and show it to the camera in real time.

	\ac{KMS} lets registering event handlers for \ac{QR} code detection. The component that detects \ac{QR} codes on \ac{KMS} is called periodically and fires the handlers with the decoded content. This mechanism does not detect if the \ac{QR} code enters or leaves the screen. We had to implement our own mechanism for detecting those events. Each user session in the server maintains a map with the contents that are present on the screen. In order to apply our algorithm more efficiently we calculate the content's hash through the \emph{md5} method. If the hash is not present in the map, it means the \ac{QR} code was entering the screen, we add that hash to the map and associate the current time to it, all the users are notified to watch that content in real-time. If the same \ac{QR} code is not detected after a time bigger then two periods we can conclude that the \ac{QR} code left the screen and we add the correspondent content into our database. Listing \ref{lst:pseudo_qrcode} shows the pseudo code for \ac{QR} code leaving detection.

@@

	In our solution, content is represented as simple text that can contain \ac{HTML}, \ac{CSS} or even \emph{JavaScript}. This content is displayed on defined intervals of time. Multiple contents can be displayed at the same time. In order to achieve that, we define layers above the video with the same size. Each layer is associated to the content.	We have taken into account that the amount of content tends to grow with time and the user should only have access to a subset of the content instead of all of it, which would be very inefficient. The content to display for each user depends on the user's position on the time-line. This position is given by an offset between the current time and the navigated time. If the user is watching the content in real-time this offset is always zero. If the user is reproducing past communications in normal playback rate, this offset is constant and, as a consequence, there is need to re-synchronize this value. If, for instance, we had to implement communication reproduction with a faster or slower playback rate, we would need to take into account the fact of this time offset not being constant.

@@

	We have used \emph{vis.js} to display out time-line. This library was created for content navigation through time, but it was not designed to be always moving automatically. We have created a background timer that performs the animation of moving the window of time bounds and user navigated time marker.

	Figure \ref{fig:timeline} shows the graphical appearance of our interactive time-line. In order to navigate through time, the user must drag and drop the time-line horizontally. When the user drops the time-line an event handler is called with the new user's time offset, which will be used to send a message to the server in order to choose the correspondent content to display.

	\begin{figure}
		\centering
		\includegraphics[width=0.95\textwidth]{figures/timeline.png}
		\caption{Interactive time-line}
		\label{fig:timeline}
	\end{figure}

	We have noticed the server time being different from client time and this created timing inconsistencies, such as showing existing recorded blocks of movie in the future. To solve this problem, the server sends its time to the client immediately after the \emph{webSocket} creation. We synchronize the time-line with the server and although it may exist a small error due to network transmission time, the graphical error is negligible.

@@

	Time annotations are a simpler way to mark points in time and share them with other users. When a user enters a conference room, the server sends all annotations so they can be displayed directly into the user time-line. When each time annotation is created, all users are notified so they can update their interfaces.

	Figure \ref{fig:annotation} shows the creation and placement of annotations on the time-line. To save the annotation the user must click on the floppy icon in order to save it and notify the conference participants.

@@

		The composite operation, as shown on figure \ref{fig:wcomposite}, is performed at \ac{KMS} and works by decoding the incoming client streams, mixing audio and video and encoding again to send back to users.

@@

		We provide a way for users to select the composite view of the conference room or the video shared by a particular user device as it can be seen on figure \ref{fig:devices}.

>>>>

	In order to create content, the user has the option to write simple movie captions without writing any code, otherwise, as mentioned before, it can write \ac{HTML}, \ac{CSS} and \emph{JavaScript}. The definition of the content's starting and ending time by the user it is not an easy task. 
	Figure \ref{fig:creation} shows the user interface for creating interactive hyper content manually.

@@

	Defining the content's time to appear in real time would require a previous user plan. Otherwise the user could make a speech and insert the content later.

	As manually content insertion is a laborious task that can be realized after the video is recorder, we provide an alternative mechanism for real time introduction of superimposed content.	In order to help the content creator to introduce and synchronize its content in real time, we allow the user to encode its content into \ac{QR} codes and show it to the camera in real time.

	\ac{KMS} lets registering event handlers for \ac{QR} code detection. The component that detects \ac{QR} codes on \ac{KMS} is called periodically and fires the handlers with the decoded content. This mechanism does not detect if the \ac{QR} code enters or leaves the screen. We had to implement our own mechanism for detecting those events. Each user session in the server maintains a map with the contents that are present on the screen. In order to apply our algorithm more efficiently we calculate the content's hash through the \emph{md5} method. If the hash is not present in the map, it means the \ac{QR} code was entering the screen, we add that hash to the map and associate the current time to it, all the users are notified to watch that content in real time. If the same \ac{QR} code is not detected after a time bigger then two periods we can conclude that the \ac{QR} code left the screen and we add the correspondent content into our database. Listing \ref{lst:pseudo_qrcode} shows the pseudo code for \ac{QR} code leaving detection.

@@

	In our solution, content is represented as simple text that can contain \ac{HTML}, \ac{CSS} or even \emph{JavaScript}. This content is displayed on defined intervals of time. Multiple contents can be displayed at the same time. In order to achieve that, we define layers above the video with the same size. Each layer is associated to the content.	We have taken into account that the amount of content tends to grow with time and the user should only have access to a subset of the content instead of all of it, which would be very inefficient. The content to display for each user depends on the user's position on the timeline. This position is given by an offset between the current time and the navigated time. If the user is watching the content in real time this offset is always zero. If the user is reproducing past communications in normal playback rate, this offset is constant and, as a consequence, there is need to re-synchronize this value. If, for instance, we had to implement communication reproduction with a faster or slower playback rate, we would need to take into account the fact of this time offset not being constant.

@@

	We have used \emph{vis.js} to display out timeline. This library was created for content navigation through time, but it was not designed to be always moving automatically. We have created a background timer that performs the animation of moving the window of time bounds and user navigated time marker.

	Figure \ref{fig:timeline} shows the graphical appearance of our interactive timeline. In order to navigate through time, the user must drag and drop the timeline horizontally. When the user drops the timeline an event handler is called with the new user's time offset, which will be used to send a message to the server in order to choose the correspondent content to display.

	\begin{figure}
		\centering
		\includegraphics[width=0.95\textwidth]{figures/timeline.png}
		\caption{Interactive timeline}
		\label{fig:timeline}
	\end{figure}

	We have noticed the server time being different from client time and this created timing inconsistencies, such as showing existing recorded blocks of movie in the future. To solve this problem, the server sends its time to the client immediately after the \emph{webSocket} creation. We synchronize the timeline with the server and although it may exist a small error due to network transmission time, the graphical error is negligible.

@@

	Time annotations are a simpler way to mark points in time and share them with other users. When a user enters a conference room, the server sends all annotations so they can be displayed directly into the user timeline. When each time annotation is created, all users are notified so they can update their interfaces.

	Figure \ref{fig:annotation} shows the creation and placement of annotations on the timeline. To save the annotation the user must click on the floppy icon in order to save it and notify the conference participants.

@@

		The composite operation, as shown on Figure \ref{fig:wcomposite}, is performed at \ac{KMS} and works by decoding the incoming client streams, mixing audio and video and encoding again to send back to users.

@@

		We provide a way for users to select the composite view of the conference room or the video shared by a particular user device as it can be seen on Figure \ref{fig:devices}.

### 2016-05-22 tese2/17_implementation_deploy.tex
[FIX] front cover typo

On table \ref{table:osspecs} we present an overview of the operating system configurations of the machine we used for deployment.

@@

	We present, on table \ref{table:softspecs}, the software we have installed inside our docker container including the versions that are in use.

>>>>

On Table \ref{table:osspecs} we present an overview of the operating system configurations of the machine we used for deployment.

@@

	We present, on Table \ref{table:softspecs}, the software we have installed inside our docker container including the versions that are in use.

### 2016-05-22 tese2/architecture.tex
until 1h test case
[FIX] front cover typo

Taking into account the goals of this project and all the technology presented so far. Our proposal is the development of a web application that provides communication and collaboration features in real-time.

@@

\begin{itemize}
 \item \textbf{Instant Messaging} - Our application must provide a simple way to send instant text messages to the conference participants.
 \item \textbf{Room management} - Conference rooms can be public or private. Public chat rooms are moderated by a group of clients which initially consists only of the room creator. This type of room has no access restrictions by default, but that can be changed by its moderators. Private chat rooms will only be visible to a defined list of clients or can be accessed by clients that have a link for that conference room.
 \item \textbf{Stream Recording} - Ability to recording and playback recorded video including all the hyper-content displayed at that time.
 \item \textbf{Stream Composition} - Our streaming server must support mixing multiple user streams into a single stream. The sound played on clients must be the composed sound of all participants but the video played can be switched to the individual or group view.
 \item \textbf{Time annotations} - Our application must give the possibility to create annotations associated to a specified time and support viewing them on a time-line. 
 \item \textbf{Content Overlay} - Our system must allow users to superimpose hyper-content to video given a range of time. This content can be continuous or discrete and interactive or non interactive.
 \item \textbf{Search} - Unified search every objects related to a conference room such as hyper-content, time annotations and users.
 \item \textbf{Content Sharing} - Our application must have the ability to share files and time links among users.
 \item \textbf{Active talker detection} - The system must enable sound detection for showing the current speaker.
 \item \textbf{Collaboration} - The web application must provide a collaborative text edition tool.
 \item \textbf{QR Code detection} - The system must interpret \emph{QR codes} in order to ease content creation.
 \item \textbf{NAT Traversal} - The system's services must be available to users that are inside a private network.
 \item \textbf{Fault tolerance} - Our system's must use a database that supports data replication.
 \item \textbf{Scalability} - Our system must be horizontally scalable, which means that load must be distributed across web, streaming and database servers.
\end{itemize}

@@

\begin{figure}[!htb]
	\centering
	\includegraphics[width=0.8\textwidth]{figures/modules.pdf}
	\caption{System Modules}
    \label{fig:modules}
\end{figure}

@@

 \item \textbf{NAT Traversal module} - \ac{STUN} and \ac{TURN} techniques used by \emph{Client} and \emph{Stream} modules during the \emph{Signaling} phase which ends by establishing the connection between them.

@@

In order to simplify our solution, we propose that the \emph{Application}, \emph{Signaling}, \emph{Stream} and \emph{Storage} modules be implemented within the same server application, so it could be easy to deploy as a single image. To this set of modules, we often call \emph{backend}.

@@

\begin{figure}[!htb]
\centering
\begin{minipage}[b]{0.45\linewidth}
	\centering
	\includegraphics[width=\textwidth]{figures/ccomposite.pdf}
	\caption{Centralized connections}
	\label{fig:central}
\end{minipage}
\quad
\begin{minipage}[b]{0.45\linewidth}
	\centering
	\includegraphics[width=\textwidth]{figures/dcomposite.pdf}
	\caption{Peer-to-Peer connections}
	\label{fig:p2p}
\end{minipage}
\end{figure}

	In this context, each client must only have one \emph{PeerConnection} to our streaming server and content shown to them is changed on demand either being it an individual or a composite view. This approach is centralized, as seen on figure \ref{fig:central}. Otherwise clients could follow a peer-to-peer connection, as seen on figure \ref{fig:p2p}, which would result on maintaining more connections and performing the composition of videos on client side.

@@

In this chapter we have shown the modules needed in order to implement our solution.

Several technologies were taken into account for implementing each module, we have studied the pros and cons of each technology and decided the architecture for our solution.

>>>>

Taking into account the goals of this project and all the technology presented so far, our proposal is the development of a web application that provides communication and collaboration features in real time.

@@

\begin{itemize}
 \item \textbf{Instant Messaging} - Our application must provide a simple way to send instant text messages to the conference participants.
 \item \textbf{Room management} - Conference rooms can be public or private. Public chat rooms are moderated by a group of clients which initially consists only of the room creator. This type of room has no access restrictions by default, but that can be changed by its moderators. Private chat rooms will only be visible to a defined list of clients or can be accessed by clients that have a link for that conference room.
 \item \textbf{Stream Recording} - Ability to record and playback recorded video including all the hyper-content displayed at that time.
 \item \textbf{Stream Composition} - Our streaming server must support mixing multiple user streams into a single stream. The sound played on clients must be the composed sound of all participants but the video played can be switched to the individual or group view.
 \item \textbf{Time annotations} - Our application must give the possibility to create annotations associated to a specified time and support viewing them on a timeline. 
 \item \textbf{Content Overlay} - Our system must allow users to superimpose hyper-content to video given a range of time. This content can be continuous or discrete and interactive or non interactive.
 \item \textbf{Search} - Unified search every objects related to a conference room such as hyper-content, time annotations and users.
 \item \textbf{Content Sharing} - Our application must have the ability to share files and time links among users.
 \item \textbf{Active talker detection} - The system must enable sound detection for showing the current speaker.
 \item \textbf{Collaboration} - The web application must provide a collaborative text edition tool.
 \item \textbf{QR Code detection} - The system must interpret \ac{QR} codes in order to ease content creation.
 \item \textbf{NAT Traversal} - The system's services must be available to users that are inside a private network.
 \item \textbf{Fault tolerance} - Our system's must use a database that supports data replication.
 \item \textbf{Scalability} - Our system must be horizontally scalable, which means that load must be distributed across web, streaming and database servers.
\end{itemize}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.8\textwidth]{figures/modules.pdf}
	\caption{System Modules}
    \label{fig:modules}
\end{figure}

@@

 \item \textbf{NAT Traversal module} - \ac{STUN} and \ac{TURN} are techniques used by \emph{Client} and \emph{Stream} modules during the \emph{Signaling} phase which ends by establishing the connection between them.

@@

In order to simplify our solution, we propose that the \emph{Application}, \emph{Signaling}, \emph{Stream} and \emph{Storage} modules be implemented within the same server application, so it could be easy to deploy as a single virtual machine image. To this set of modules, we often call \emph{backend}.

@@

\begin{figure}
\centering
\begin{minipage}[b]{0.45\linewidth}
	\centering
	\includegraphics[width=\textwidth]{figures/ccomposite.pdf}
	\caption{Centralized connections}
	\label{fig:central}
\end{minipage}
\quad
\begin{minipage}[b]{0.45\linewidth}
	\centering
	\includegraphics[width=\textwidth]{figures/dcomposite.pdf}
	\caption{Peer-to-Peer connections}
	\label{fig:p2p}
\end{minipage}
\end{figure}

	In this context, each client must only have one \emph{PeerConnection} to our streaming server and content shown to them is changed on demand either being it an individual or a composite view. This approach is centralized, as seen on Figure \ref{fig:central}. Otherwise clients could follow a peer-to-peer connection, as seen on Figure \ref{fig:p2p}, which would result on maintaining more connections and performing the composition of videos on client side.

@@

In this chapter we have described the modules needed in order to implement our solution.

Several technologies were taken into account for implementing each module. We have studied the pros and cons of each technology and decided the architecture for our solution.

### 2016-05-22 tese2/evaluation.tex
[FIX] front cover typo

With this results we conclude that if we want to scale our storage solution using the \emph{MongoDB}'s cluster configuration, both \emph{Kurento Repository} and \ac{KMS} should be installed on the same machine, as depicted on figure \ref{fig:scale2}, because the loopback interface can handle bigger transfer rates than the remaining network interfaces. Installing the repository on the same machine as a database node does not ensure that recorded videos are stored in the same machine, for this reason we would prefer installing \ac{KMS} and \emph{Kurento Repository} on the same machine.

@@

Figure \ref{fig:test_full_features_cpu_zoom} is the same as figure \ref{fig:test_full_features_cpu} but zoomed over \emph{MongoDB}, \emph{Java} and \emph{Kurento Repository}. As we can see there are periodic processing peaks every ten seconds that are due to block recording. \ac{KMS} is responsible for most \ac{CPU} usage.

@@

We have also performed two consecutive test cases in order to understand if we the influence of the first test case over the second, as observed in figure \ref{fig:test_two_times_cpu}, there is no \ac{CPU} influence between two test cases.

@@

On the other hand due to memory recycling techniques we can observe in figure \ref{fig:test_two_times_mem} that some of the memory that was allocated in the first test was reused in the second case.

@@

The initial users that tested our solution had difficulties in the first task when finding new friendship requests and adding new friends, as friendship request were only possible to access from the top bar and new user profiles were only accessible through the search bar. In order to solve this problem we have added a menu for adding new users in the friends list and another near the friends list as it can be seen on figure \ref{fig:test_ui_01_02_03}.

@@

On the second task one user clicked on the friends list for adding a friend to a room and, as a consequence, left the conference room to the user profile. We solved this problem by showing a pop-up with the user profile and an additional button to add the user to the conference room as it can be seen on figure \ref{fig:test_ui_04}.

@@

On the third task we noticed that users were not expecting to search the content directly from the search bar, instead they used the time-line.

On the fourth task the users did not placed their annotations on right place. We only provide one way to place annotations, which is by dragging them on the time-line. 
After creating an annotation, users also did not understand that they had to save their changes on the time-line. We solved this problem by saving automatically each time the user changed any annotation. The old user interface can be seen on figure \ref{fig:test_ui_05}.

@@

\begin{itemize}
\item Giving feedback to user when performing operations such as create superimposed content and save the collaborative editor content.
\item Starting with our time-line more zoomed in order to give more sensation of time passing.
\item Create content with starting time and duration, instead of ending time.
\end{itemize}

@@

To this end, with regard to optimal task duration and minimal clicks, we obtained the values shown in table \ref{table:optimal}.

@@

Another weak aspect was our content editor, which, in fact, we recognize is difficult to work with, mostly due to the amount of information that is necessary to create a synchronized content (starting time, duration and content itself). Some users have suggested that the content should also be present on the time-line so they could be easily dragged and resized (on time).

We are aware that placing content on the time-line will reduce our solutions performance, especially when there is a relatively large amount of content, due to the content that is present on the time-line being loaded all at once. Although, we recognize that for some cases (relatively low amount of content), displaying the content on the time-line could not have a great impact on our solutions performance, we choose not to implement this.

>>>>

With this results we conclude that if we want to scale our storage solution using the \emph{MongoDB}'s cluster configuration, both \emph{Kurento Repository} and \ac{KMS} should be installed on the same machine, as depicted on Figure \ref{fig:scale2}, because the loopback interface can handle bigger transfer rates than the remaining network interfaces. Installing the repository on the same machine as a database node does not ensure that recorded videos are stored in the same machine, for this reason we would prefer installing \ac{KMS} and \emph{Kurento Repository} on the same machine.

@@

Figure \ref{fig:test_full_features_cpu_zoom} is the same as Figure \ref{fig:test_full_features_cpu} but zoomed over \emph{MongoDB}, \emph{Java} and \emph{Kurento Repository}. As we can see there are periodic processing peaks every ten seconds that are due to block recording. \ac{KMS} is responsible for most \ac{CPU} usage.

@@

We have also performed two consecutive test cases in order to understand if we the influence of the first test case over the second, as observed in Figure \ref{fig:test_two_times_cpu}, there is no \ac{CPU} influence between two test cases.

@@

On the other hand due to memory recycling techniques we can observe in Figure \ref{fig:test_two_times_mem} that some of the memory that was allocated in the first test was reused in the second case.

@@

The initial users that tested our solution had difficulties in the first task when finding new friendship requests and adding new friends, as friendship request were only possible to access from the top bar and new user profiles were only accessible through the search bar. In order to solve this problem we have added a menu for adding new users in the friends list and another near the friends list as it can be seen on Figure \ref{fig:test_ui_01_02_03}.

@@

On the second task one user clicked on the friends list for adding a friend to a room and, as a consequence, left the conference room to the user profile. We solved this problem by showing a pop-up with the user profile and an additional button to add the user to the conference room as it can be seen on Figure \ref{fig:test_ui_04}.

@@

On the third task we noticed that users were not expecting to search the content directly from the search bar, instead they used the timeline.

On the fourth task the users did not placed their annotations on right place. We only provide one way to place annotations, which is by dragging them on the timeline. 
After creating an annotation, users also did not understand that they had to save their changes on the timeline. We solved this problem by saving automatically each time the user changed any annotation. The old user interface can be seen on Figure \ref{fig:test_ui_05}.

@@

\begin{itemize}
\item Giving feedback to user when performing operations such as create superimposed content and save the collaborative editor content.
\item Starting with our timeline more zoomed in order to give more sensation of time passing.
\item Create content with starting time and duration, instead of ending time.
\end{itemize}

@@

To this end, with regard to optimal task duration and minimal clicks, we obtained the values shown in Table \ref{table:optimal}.

@@

Another weak aspect was our content editor, which, in fact, we recognize is difficult to work with, mostly due to the amount of information that is necessary to create a synchronized content (starting time, duration and content itself). Some users have suggested that the content should also be present on the timeline so they could be easily dragged and resized (on time).

We are aware that placing content on the timeline will reduce our solutions performance, especially when there is a relatively large amount of content, due to the content that is present on the timeline being loaded all at once. Although, we recognize that for some cases (relatively low amount of content), displaying the content on the timeline could not have a great impact on our solutions performance, we choose not to implement this.

### 2016-05-22 tese2/implementation.tex
[FIX] front cover typo

Then are going to describe how we show hyper-content to users, namely the multiple ways to create hyper-content and the algorithm behind the user interface synchronization, the security flaws of our content displaying mechanism and a possible solution to overcome vulnerabilities.

Not less important we also are going to describe how we have implemented our application time-line and the functionalities above it such as time manipulation and annotations management. Among other different functionalities we also are going to describe how we perform stream composition, synchronization of our collaborative text editor and implementation of our instant messenger.

>>>>

Afterwards we are going to describe how we show hyper-content to users, namely the multiple ways to create hyper-content and the algorithm behind the user interface synchronization, the security flaws of our content displaying mechanism and a possible solution to overcome vulnerabilities.

Not less important we also are going to describe how we have implemented our application timeline and the functionalities above it such as time manipulation and annotations management. Among other different functionalities we also are going to describe how we perform stream composition, synchronization of our collaborative text editor and implementation of our instant messenger.

### 2016-05-22 tese2/introduction.tex
[FIX] front cover typo

	Since the early days of Human History, we tried to communicate over far locations, from smoke signals to letters delivered by messengers. Real-time communications were limited or even nonexistent. Despite all the efforts made to improve communications, written communication could never replace face to face communication.
	With the advent of the telephone network, communications have taken a very important step for us to feel more connected with whom we communicate. Still, only the human voice was not enough, and the invention of cameras and consequent video digitalization were a huge step for real-time communications.

@@

    Furthermore, real-time communication applications can make a significant difference on business, education and health sectors by providing tools for developing teaching and learning online, teamworking and socializing web applications.

@@

	Therefore, a real-time system is a huge source of information that requires much attention from its users. In this context, an application that provides a way to remember our past communications would be a strong tool for not only to catch what we lost but also to enhance our knowledge.

>>>>

	Since the early days of Human History, we tried to communicate over far locations, from smoke signals to letters delivered by messengers. Real-time communications were limited or even nonexistent. Despite all the efforts made to improve communications, written communication could never replace face to face communication.
	With the advent of the telephone network, communications have taken a very important step for us to feel more connected with whom we communicate. Still, only the human voice was not enough, and the invention of cameras and consequent video digitalization were a huge step for real time communications.

@@

    Furthermore, real time communication applications can make a significant difference on business, education and health sectors by providing tools for developing teaching and learning online, teamworking and socializing web applications.

@@

	Therefore, a real time system is a huge source of information that requires much attention from its users. In this context, an application that provides a way to remember our past communications would be a strong tool for not only to catch what we lost but also to enhance our knowledge.

### 2016-05-22 tese2/xthesis.tex
caneco
[FIX] front cover typo

\emph{WebRTC} technology allows real-time communications between web browsers without the need to install additional software. The nature of web browser applications already follows the hypermedia concept, which makes \emph{WebRTC} the ideal technology to apply the hyper-linked communications concepts.
The web browser platform provides an abstraction layer that makes it possible to create applications that run independently from the operating system.
The native support for \emph{WebRTC} in operating systems extends its usage to outside the web browser, allowing for the exploration of functionalities for which web browsers provide poor support, such as video recording and massive information storage.

@@

	\emph{otJS} is a \emph{JavaScript} library that only implements operation transformations over plain text on the client side and requires implementing the content's persistent storage. Besides this drawback, this library is very flexible because it's not tied to a specific database or server side technology.

@@

Taking into account the goals of this project and all the technology presented so far. Our proposal is the development of a web application that provides communication and collaboration features in real-time.

@@

The server receives and processes the offer and sets the \emph{remote session description} to its client associated \gls{WebRTC} endpoint. Then a \emph{local session description} is created on the server and sent back to the client, after that the server tries to gather \gls{ICE} candidates.

@@

	With server side recording, the user would maintain always the same stream \gls{URL} even if it is playing real-time video or reproducing recorded video. It is \gls{KMS} that sends different content through that stream. When a user desires to play recorded video, a \emph{webSocket} message is sent specifying the time and the intended user id. The server performs the calculations in order to find a block that intersects the requested time, plays it and when finished, the next part is automatically played without the user intervention.

@@

	As manually content insertion is a laborious task that can be realized after the video is recorder, we provide an alternative mechanism for real time introduction of superimposed content.	In order to help the content creator to introduce and synchronize its content in real-time, we allow the user to encode its content into \gls{QR} codes and show it to the camera in real time.

>>>>

\emph{WebRTC} technology allows real time communications between web browsers without the need to install additional software. The nature of web browser applications already follows the hypermedia concept, which makes \emph{WebRTC} the ideal technology to apply the hyper-linked communications concepts.
The web browser platform provides an abstraction layer that makes it possible to create applications that run independently from the operating system.
The native support for \emph{WebRTC} in operating systems extends its usage to outside the web browser, allowing for the exploration of functionalities for which web browsers provide poor support, such as video recording and massive information storage.

@@

	\emph{otJS} is a \emph{JavaScript} library that only implements operation transformations over plain text on the client side and requires implementing the content's persistent storage. Besides this drawback, this library is very flexible because it is not tied to a specific database or server side technology.

@@

Taking into account the goals of this project and all the technology presented so far. Our proposal is the development of a web application that provides communication and collaboration features in real time.

@@

The server receives and processes the offer and sets the \emph{remote session description} to its client associated \gls{WebRTC} endpoint. Then a \emph{local session description} is created on the server and sent back to the client. After that, the server tries to gather \gls{ICE} candidates.

@@

	With server side recording, the user would maintain always the same stream \gls{URL} even if it is playing real time video or reproducing recorded video. It is \gls{KMS} that sends different content through that stream. When a user desires to play recorded video, a \emph{webSocket} message is sent specifying the time and the intended user id. The server performs the calculations in order to find a block that intersects the requested time, plays it and when finished, the next part is automatically played without the user intervention.

@@

	As manually content insertion is a laborious task that can be realized after the video is recorder, we provide an alternative mechanism for real time introduction of superimposed content.	In order to help the content creator to introduce and synchronize its content in real time, we allow the user to encode its content into \gls{QR} codes and show it to the camera in real time.
